better title eventually

### 2015-05-11 cs261n-paper/paper.tex
added a survey questions blurb.

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item What session did you attend?  
\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) \\
\item What is your gender? 
\item What is your age? 
\item Please select your highest level of education. 
\item What is your current occupation? \\
\item How familiar were you with Tor prior to this study? 
\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
\item Did anything unexpected happen while using Tor? 
\item What, if any, of the following could use improvement? 
\item Based on your experience, would you use Tor again? \\
\item How many hours a week would you say you spend on the internet? 
\item How concerned are you about your privacy on the Internet?
\item How concerned are you about staying anonymous on the internet?
\item How concerned are you about being censored while you browse the Internet? \\
\item How familiar are you with computer security? 
\item What kinds of computer security software do you use? 
\end{enumerate}

>>>>

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item What session did you attend?  
\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) 
\item What is your gender? 
\item What is your age? 
\item Please select your highest level of education. 
\item What is your current occupation?*
\item How familiar were you with Tor prior to this study? 
\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
\item Did anything unexpected happen while using Tor?*
\item What, if any, of the following could use improvement?*
\item Based on your experience, would you use Tor again?*
\item How many hours a week would you say you spend on the internet? 
\item How concerned are you about your privacy on the Internet?
\item How concerned are you about staying anonymous on the internet?
\item How concerned are you about being censored while you browse the Internet? 
\item How familiar are you with computer security? 
\item What kinds of computer security software do you use? 
\end{enumerate}

Questions marked with asterisks are open-ended questions. All other questions are multiple choice, whether they be radio buttons, check boxes, or a drop down menu. For additional details regarding answer inputs, we refer you to our online survey linked above.
